When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2020-11-18 code/Submissionv4.Rmd
commit

header-includes:
    - \usepackage{setspace}
    - \usepackage{multirow}
    - \usepackage{indentfirst}

@@

@@

```{r, include = FALSE, echo = FALSE}
library("here")       # file paths
library("tidyverse")  # workhorse package
library("tidylog")
library("kableExtra")
library("knitr")
library("ggdag")
library("dagitty")
library("gridExtra")
library("broom")
library("dplyr")
library("reshape2")
```
\newpage

@@

dataset <- read_csv(here("data", "MilEditorials10Aug.csv"))
dataset %>% print()
# Only read in the first 344 rows - is there a better way to get rid of N/A data?
# Replace NA with 0 in the data for variables War_Ops thru Fig_Nme
adjdataset <- dataset[1:344,] %>%
  mutate_at(
    .vars = vars(War_Ops:Fig_Nme),
    .funs = ~ case_when(is.na(.) ~0, TRUE ~ 1)
) %>% mutate(
    PubYr = lubridate::year(PubDate)
) %>% view()

@@

# count the number of observations by type of binary variable and store as new dataframe
countbytype  <- adjdataset %>% count(War_Ops, Trp_Clt, Str_Adv, MilPSoc, Dom_P, Fig_Nme) 
countbytype

@@

adjdataset <- adjdataset %>% 
  group_by(PubYr) %>% 
  mutate(Yrcount=n()) 
```

@@

ggplot(data=adjdataset, aes(x=PubYr, y=Yrcount)) + geom_point() + geom_line() + geom_smooth(method="loess") + labs(
  x="Year", 
  y="count", 
  title="Figure Two: Number of Op-Eds Published by Retired\n Military Officers (WSJ, NYT, WaPo, USA Today, and LA Times",
  subtitle= "1979-2020",
  caption="Note: As of 31 August 2020"
  ) + scale_x_continuous(limits=c(1979, 2020)) + scale_y_continuous(limits=c(-7, 28)) + 
geom_vline(xintercept = 1981, size=.2, colour="tomato") + 
  geom_vline(xintercept=1989, size=.2, colour="tomato") + 
  geom_vline(xintercept=1993, size=.2, colour="dodgerblue") + geom_vline(xintercept=2001, size=.2, colour="tomato") + 
  geom_vline(xintercept=2009, size=.2, colour="dodgerblue") +
  geom_vline(xintercept=2017, size=.2, colour="tomato") +
  geom_text(aes(x=1981, label="Reagan",y=-5), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1989, label="Bush 41",y=-5), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1993, label="Clinton",y=-5), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2001, label="Bush 43",y=-5), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2009, label="Obama",y=-5), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2017, label="Trump",y=-5), colour="tomato", angle=90, vjust=1, text=element_text(size=9))

@@

# Show all articles and authors who published articles on Social Policy, Political Parties, and Administrations/Political Figures
rem_obs <-adjdataset %>% arrange(PubYr) %>% 
  filter(MilPSoc==1 | Dom_P==1 | Fig_Nme==1 )  %>% 
  select (Author, Title, Source, PubYr, MilPSoc, Dom_P, Fig_Nme) %>% 
  view()

# Create a Variable Called case-count that counts the number of times by publishing year an article published 
# regarding social policy, domestic policy, or political figures/administrations occurs

adj2dataset <- adjdataset %>% group_by(PubYr) %>% 
  mutate(
    case_count=sum(MilPSoc ==1 | Dom_P==1 | Fig_Nme==1), 
    yr_total_count=sum(War_Ops==1 | Trp_Clt==1| Str_Adv==1 | MilPSoc ==1 | Dom_P==1 | Fig_Nme==1),
    prop_yr=(case_count/yr_total_count)
  ) %>% view()

# Present Results of Result and Justification
secondlayer_obs <-adjdataset %>% arrange(PubYr) %>% 
  filter(MilPSoc==1 | Dom_P==1 | Fig_Nme==1 )  %>% 
  select (Author, Title, Source, PubYr, Ques_Prof, Justification) %>% 
  view()
```

\singlespace
```{r table4, fig.align = "center", include=TRUE, echo=FALSE}
#Need to adjust the width and spacing of this table
secondlayer_obs %>%
  kable(format="latex", caption="Potentially Unprofessional Op-Ed Pieces By Retired Military Officers, 1979-2020", longtable=T) %>%
  kable_styling(font_size=10, latex_options="striped", repeat_header_continued=T) %>% 
  column_spec(1, width="9.5em") %>% 
  column_spec(2, width="15em") %>% 
  column_spec(3:4, width="2.5em") %>%
  column_spec(5, width="5em") %>%
  column_spec(6, width="6em") %>%
  row_spec(0, bold=T)
```
\doublespace

@@

```{r build plots, include = FALSE, echo=FALSE}
plot1<- ggplot(data=adj2dataset, mapping=aes(x=PubYr, y=case_count)) + geom_point() + geom_smooth() + labs(x="Year", y="Number", color=NULL) + geom_vline(xintercept = 1981, size=.2, colour="tomato") + 
  geom_vline(xintercept=1989, size=.2, colour="tomato") + 
  geom_vline(xintercept=1993, size=.2, colour="dodgerblue") + geom_vline(xintercept=2001, size=.2, colour="tomato") + 
  geom_vline(xintercept=2009, size=.2, colour="dodgerblue") +
  geom_vline(xintercept=2017, size=.2, colour="tomato") +
  geom_text(aes(x=1981, label="Reagan",y=3), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1989, label="Bush 41",y=3), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1993, label="Clinton",y=3), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2001, label="Bush 43",y=5), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2009, label="Obama",y=5), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2017, label="Trump",y=-1), colour="tomato", angle=90, vjust=1, text=element_text(size=9))

plot2 <- ggplot(data=adj2dataset, mapping=aes(x=PubYr, y=prop_yr)) + geom_point() + geom_smooth() + labs(x="Year", y="Proportion", color=NULL)+ geom_vline(xintercept = 1981, size=.2, colour="tomato") + 
  geom_vline(xintercept=1989, size=.2, colour="tomato") + 
  geom_vline(xintercept=1993, size=.2, colour="dodgerblue") + geom_vline(xintercept=2001, size=.2, colour="tomato") + 
  geom_vline(xintercept=2009, size=.2, colour="dodgerblue") +
  geom_vline(xintercept=2017, size=.2, colour="tomato") +
  geom_text(aes(x=1981, label="Reagan",y=.25), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1989, label="Bush 41",y=.25), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1993, label="Clinton",y=.25), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2001, label="Bush 43",y=.5), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2009, label="Obama",y=.5), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2017, label="Trump",y=.55), colour="tomato", angle=90, vjust=1, text=element_text(size=9))

@@

```{r figure 3, include=TRUE, warning= FALSE, message = FALSE, echo=FALSE}
grid.arrange(plot1, plot2, ncol=2, top="Figure 3: Number(L) and Proportion (R) of Op-Eds Published\n by Retired Military Officers on Non-Traditional Military Topics, 1979-2020***", bottom="*** Topics include: Social Policy which Impacts the Military,\n Domestic Policy, and Political Administrations/Figures")
```

@@

```{r figure 4, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#adjust the data to account for polarization by creating a new dataset called polaradjdataset.  
#In this dataset, create variables that capture ideological distance in each the House and Senate along
#each of the two dimensions according to Poole and Rosenthal's DW-NOMINATE data

polaradjdataset <-adjdataset %>% mutate (
  House_distance_dim1=abs(House_Dem_mean_nom1-House_Rep_mean_nom1),
  Sen_distance_dim1=abs(Sen_Dem_mean_nom1-Sen_Rep_mean_nom1),
  House_distance_dim2=abs(House_Dem_mean_nom2-House_Rep_mean_nom2),
  Sen_distance_dim2=abs(Sen_Dem_mean_nom2-Sen_Rep_mean_nom2)
) %>% view()

@@

#Now I Prep the data that I need to analyze polarization levels.  I will try first by 
# eliminating the NA values but I will do this by indexing the first 334 rows of the 
# data, which corresponds to the number of observations that I have.  I do this by #creating a new data set called slimdata.

# Note: this is sloppy.  There has to be a better way to get rid of NA values.

slimdata <- polaradjdataset[1:344,] %>% 
  view()

#next, conduct logit regressions where the DV is values of Ques_Prof
# include two IVs: house_distance_dim1 and Inst_Cred_Gallup

@@

logmodel1 <- glm(
  Ques_Prof ~ Inst_Cred_Gallup + House_distance_dim1, 
  family=binomial(link="logit"), 
  data=slimdata
  )

tidy(logmodel1)
glance(logmodel1)

# now  make predictions.

# the first prediction data keeps credibility constant and varies house_distance_dim1 from it's min to its max
predictiondata <- tibble(House_distance_dim1=seq(min(slimdata$House_distance_dim1), max(slimdata$House_distance_dim1), by=.01), Inst_Cred_Gallup = mean(slimdata$Inst_Cred_Gallup)) %>%
crossing(Ques_Prof = c(0,1))

predictiondata

# the second prediction keeps credibility constant but varies house_distance_dim1 from its min to .99, which is a 
# perfectly reasonable expectation of the next 10-20 years of increasing political polarization in Congress. 
predictiondatafut <- tibble(House_distance_dim1=seq(min(slimdata$House_distance_dim1), .99, by=.01), Inst_Cred_Gallup = mean(slimdata$Inst_Cred_Gallup)) %>%
crossing(Ques_Prof = c(0,1))

predictiondatafut

# actual prediction data now with code.  Create variables that tie the model together. #Create Variables .prob, conf.low, conf.high, and pred_final_rec

#augment first prediction
augment(logmodel1, newdata = predictiondata)

#augment second prediction
augment(logmodel1, newdata = predictiondatafut)

# first prediction: house_distance_dim1 from min to max
predictions <- augment(logmodel1, newdata=predictiondata) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  )

predictions %>% arrange(.prob, .fitted, Ques_Prof, desc(.fitted)) %>% 
  view()

# second prediction: house_distance_dim1 from min to a predicted value of .99
predictions2 <- augment(logmodel1, newdata=predictiondatafut) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions2 %>% arrange(.prob, .fitted, Ques_Prof, desc(.fitted)) %>% 
  view()

# now let's try some graphs
# notice that the predictions are not in (0, 1)
ggplot(predictions) +
  aes(x = .fitted) +
  geom_histogram()

ggplot(predictions2) +
  aes(x = .fitted) +
  geom_histogram()
# if we wanted predictions on the probability scale,
#   we predict on the log scale,
#   then apply inverse-logit (logistic CDF)
# use plogis(): cumulative probability of the logistic distribution

# demonstration: scatter log odds (x) and predicted probability (y)
# with 95% CIs
# (CIs don't look smooth in this example because .se.fit depends on X data)
predictions %>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth()

predictions2 %>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth()

# model2

logmodel2 <- glm(
  Ques_Prof ~ House_distance_dim1 + Inst_Cred_Gallup, 
  family=binomial(link="logit"), 
  data=slimdata
  )

tidy(logmodel2)
glance(logmodel2)

# now  make prediction data using the mean institutional credibility scores.  Vary #institutional credibilty and hold political polarization constant.

predictiondata2 <- tibble(Inst_Cred_Gallup=seq(min(slimdata$Inst_Cred_Gallup), max(slimdata$Inst_Cred_Gallup), by=1), House_distance_dim1 = mean(slimdata$House_distance_dim1)) %>%
crossing(Ques_Prof = c(0,1))

predictiondata2

# actual prediction data now with code.  Create variables that tie the model together. #Create Variables .prob, conf.low, conf.high, and pred_final_rec

augment(logmodel2, newdata = predictiondata2)

predictions2 <- augment(logmodel2, newdata=predictiondata2) %>% 
  mutate(
    .prob=plogis(.fitted),
    conf.low = plogis(.fitted -(qnorm(.975) * .se.fit)),
    conf.high = plogis(.fitted + (qnorm(.975) * .se.fit)),
    pred_final_rec = case_when(
      .prob >= .5 ~ "Likely Violation of Professionalism",
      .prob < .5 ~ "Violation of Professionalism not likely"
    )
  ) 
predictions2 %>% arrange(.prob, .fitted, Ques_Prof, desc(.fitted)) %>% 
  view()
```

```{r fig5, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
predictions%>%
  ggplot() +
  aes(x = .fitted, y = .prob) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_smooth() + labs(
    x="log Mean Distance Between Republicans and Democrats\n in the US House of Representatives, 1979-2020",
    y="Predicted Probability of A Retired Military Officer\n Publishing an Op-Ed that Violates Military Professionalism",
    title="Figure 5: The Predicted Impact of Political Polarization\n on Military Professionalism"
  )
```

>>>>

header-includes:
    - \usepackage{setspace}
    - \usepackage{multirow}
    - \usepackage{indentfirst}
    - \usepackage{caption}

@@

\captionsetup[table]{labelformat=empty}

@@

```{r, include = FALSE, echo = FALSE}
library("here")       # file paths
library("tidyverse")  # workhorse package
library("tidylog")
library("kableExtra")
library("knitr")
library("ggdag")
library("dagitty")
library("gridExtra")
library("broom")
library("dplyr")
library("reshape2")
library(stargazer)
```
\newpage

@@

dataset <- read_csv(here("data", "MilEditorials.csv"))
dataset %>% print()
# Only read in the first 354 rows - is there a better way to get rid of N/A data?

# Replace NA with 0 in the data for variables letter_ed to online_only, and leg_act #to role
adjdataset <- dataset[1:353,] %>%
  mutate_at(
    .vars = vars(letter_ed:online_only, Leg_Act:Role),
    .funs = ~ case_when(is.na(.) ~0, TRUE ~ 1)
) %>% mutate(
    PubYr = lubridate::year(PubDate)
) %>% view()

@@

# count the number of observations by type of binary variable and store as new dataframe
countbytype  <- adjdataset %>% 
  count(Topic) %>% print()

# count the number of observations by source
countbysource <- adjdataset %>% 
  count(Source) %>% print()

@@

adjdataset <- adjdataset %>% 
  group_by(PubYr) %>% 
  mutate(Yrcount=n()) %>% 
  view()
```

@@

ggplot(data=adjdataset, aes(x=PubYr, y=Yrcount)) + geom_point() + geom_line() + geom_smooth(method="loess") + labs(
  x="Year", 
  y="yearly count", 
  title="Figure Two: Number of Op-Eds Published by Retired Military\n Officers (WSJ, NYT, WaPo, USA Today, LA Times)",
  subtitle= "1979-2020",
  caption="Note: As of 29 October 2020"
  ) + scale_x_continuous(limits=c(1979, 2020)) + scale_y_continuous(limits=c(-7, 28)) + 
geom_vline(xintercept = 1981, size=.2, colour="tomato") + 
  geom_vline(xintercept=1989, size=.2, colour="tomato") + 
  geom_vline(xintercept=1993, size=.2, colour="dodgerblue") + geom_vline(xintercept=2001, size=.2, colour="tomato") + 
  geom_vline(xintercept=2009, size=.2, colour="dodgerblue") +
  geom_vline(xintercept=2017, size=.2, colour="tomato") +
  geom_text(aes(x=1981, label="Reagan",y=10), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1989, label="Bush 41",y=15), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1993, label="Clinton",y=20), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2001, label="Bush 43",y=-2), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2009, label="Obama",y=-2), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2017, label="Trump",y=-2), colour="tomato", angle=90, vjust=1, text=element_text(size=9))

@@

# Show all articles and authors who published articles on Domestic Policy and Social Policy 
adjdataset %>% arrange(PubYr) %>% 
  filter(Topic=="DomesticPolicy" | Topic=="SocialPolicy")  %>% 
  select (Author, Title, Source, PubYr, Topic) %>% 
  print()

# Show all articles where Leg_Act, Crit_Insub, or Endorse_Partisan was equal to 1
## (in other words, articles in which the author called for legislative activity, criticized, or made
## an explicitly partisan statement)

adjdataset %>% arrange(PubYr) %>% 
  filter(Leg_Act== 1 | Crit_Insub== 1 | Endorse_Partisan ==1)  %>% 
  select (Author, Title, Source, PubYr, Topic, Leg_Act, Crit_Insub, Endorse_Partisan) %>% 
  print()

# create a df called quest_prof that contains articles that either criticized or were #expressly partisan, as well as whether someone was in a role at the time that may have # made such behavior ok

quest_prof <-adjdataset %>% arrange(PubYr, Topic) %>% 
  filter(Crit_Insub== 1 | Endorse_Partisan ==1)  %>% 
  select (Author, Title, Source, PubYr, Topic, Crit_Insub, Endorse_Partisan, Role) %>% 
  view()

## Do a couple of things here.  Create several new variables.  
# The first is a variable called case-count that counts the number of times by publishing #year an article published that calls for legislative action, criticizes or is #insubordinate, or is blatantly partisan. The second variable, prop_yr, is simply a 
# proportion of annual publications where these conditions hold true.
# The third variable is called dom_pol_count which counts the number of publications
# by publishing year that are written on topics of domestic policy, and the fourth 
# variable is a proportion of this type of article by year.

adjdataset <- adjdataset %>% group_by(PubYr) %>% 
  mutate(
    case_count=sum(Leg_Act ==1 | Crit_Insub==1 | Endorse_Partisan==1), 
    prop_yr=(case_count/Yrcount),
    dom_pol_count=sum(Topic=="DomesticPolicy"),
    dom_pol_prop=(dom_pol_count/Yrcount)
  ) %>% view()

# Now create two variables, leg_crit_part and crit_part that take a 1 if certain 
# conditions are met.  This will come in handy for the glm regressions that
# will be conducted later.

adjdataset <- adjdataset %>% 
  mutate(
    leg_crit_part=case_when(
      (Leg_Act==1 | Crit_Insub ==1 | Endorse_Partisan==1 & Role ==0) ~ 1,
      (Leg_Act != 1 & Crit_Insub != 1 & Endorse_Partisan !=1 | Role==1) ~ 0
    ),
    crit_part=case_when(
      (Crit_Insub ==1 | Endorse_Partisan==1 & Role ==0) ~ 1,
      (Crit_Insub != 1 & Endorse_Partisan != 1 | Role ==1) ~ 0
    )
  ) %>% 
  view()

\singlespace
```{r table4, fig.align = "center", include=TRUE, echo=FALSE}
#Need to adjust the width and spacing of this table
quest_prof %>%
  kable(format="latex", caption="Op-Eds authored by Retired Military Officers that Strongly Criticized Civilian Leaders, or were Expressly Partisan, 1979-2020", longtable=T) %>%
  kable_styling(font_size=10, latex_options="striped", repeat_header_continued=T) %>% 
  column_spec(1, width="9.5em") %>% 
  column_spec(2, width="15em") %>% 
  column_spec(3:4, width="2.5em") %>%
  column_spec(5, width="5em") %>%
  column_spec(6, width="6em") %>%
  row_spec(0, bold=T)
```
\doublespace

@@

```{r build plots, include = FALSE, echo=FALSE}
plot1<- ggplot(data=adjdataset, mapping=aes(x=PubYr, y=prop_yr)) + geom_point() + geom_smooth() + labs(x="Year", y="Annual Proportion", color=NULL) + geom_vline(xintercept = 1981, size=.2, colour="tomato") + 
  geom_vline(xintercept=1989, size=.2, colour="tomato") + 
  geom_vline(xintercept=1993, size=.2, colour="dodgerblue") + geom_vline(xintercept=2001, size=.2, colour="tomato") + 
  geom_vline(xintercept=2009, size=.2, colour="dodgerblue") +
  geom_vline(xintercept=2017, size=.2, colour="tomato") +
  geom_text(aes(x=1981, label="Reagan",y=.2), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1989, label="Bush 41",y=.2), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1993, label="Clinton",y=.4), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2001, label="Bush 43",y=.3), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2009, label="Obama",y=.4), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2017, label="Trump",y=0), colour="tomato", angle=90, vjust=1, text=element_text(size=9))

plot2 <- ggplot(data=adjdataset, mapping=aes(x=PubYr, y=dom_pol_prop)) + geom_point() + geom_smooth() + labs(x="Year", y="Proportion", color=NULL)+ geom_vline(xintercept = 1981, size=.2, colour="tomato") + 
  geom_vline(xintercept=1989, size=.2, colour="tomato") + 
  geom_vline(xintercept=1993, size=.2, colour="dodgerblue") + geom_vline(xintercept=2001, size=.2, colour="tomato") + 
  geom_vline(xintercept=2009, size=.2, colour="dodgerblue") +
  geom_vline(xintercept=2017, size=.2, colour="tomato") +
  geom_text(aes(x=1981, label="Reagan",y=.25), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1989, label="Bush 41",y=.25), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=1993, label="Clinton",y=.25), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2001, label="Bush 43",y=.3), colour="tomato", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2009, label="Obama",y=.3), colour="dodgerblue", angle=90, vjust=1, text=element_text(size=9)) + 
  geom_text(aes(x=2017, label="Trump",y=-.05), colour="tomato", angle=90, vjust=1, text=element_text(size=9))

@@

```{r figure 3, include=TRUE, warning= FALSE, message = FALSE, echo=FALSE}
grid.arrange(plot1, plot2, ncol=2, top="Figure 3: Proportion of Op-Eds Published Which\n (L) Call for Legislative Action, Criticize Civilian Leaders, or are Partisan\n in nature; or (R) Address Domestic Political Topics")
```

@@

```{r figure 4, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
#adjust the data to account for polarization by creating a new dataset called polaradjdataset.  
#In this dataset, create variables that capture ideological distance in each the House and Senate along each of the two dimensions according to Poole and Rosenthal's DW-NOMINATE data

# scale the data by multiplying by 100

polaradjdataset <-adjdataset %>% mutate (
  House_distance_dim1=abs(House_Dem_mean_nom1-House_Rep_mean_nom1)*100,
  Sen_distance_dim1=abs(Sen_Dem_mean_nom1-Sen_Rep_mean_nom1)*100,
  House_distance_dim2=abs(House_Dem_mean_nom2-House_Rep_mean_nom2)*100,
  Sen_distance_dim2=abs(Sen_Dem_mean_nom2-Sen_Rep_mean_nom2)*100
) %>% view ()

@@

#next, conduct logit regressions where the DV is first, values of leg_crit_part and
# then, where the DV is crit_part

@@

mod1 <- glm(leg_crit_part ~ Inst_Cred_Gallup + House_distance_dim1 + AuthSex + AuthRank + Topic, 
  family=binomial(link="logit"), 
  data=polaradjdataset
  )

summary(mod1)
tidy(mod1)
glance(mod1)

# model 2
mod2 <- glm(crit_part ~ Inst_Cred_Gallup + House_distance_dim1 + AuthSex + AuthRank + Topic, 
    family=binomial(link="logit"),
    data=polaradjdataset
    )

summary(mod2)
tidy(mod2)
glance(mod2)

# model 3 - remove topic as an IV because there is significant correlation between
# one type of topic (domestic policy) and the DV

mod3 <- glm(leg_crit_part ~ Inst_Cred_Gallup + House_distance_dim1 + AuthSex + AuthRank,
    family=binomial(link="logit"),
    data=polaradjdataset
    )

summary(mod3)
tidy(mod3)
glance(mod3)

# model 4 - same as mod3, but change the DV to crit_part

mod4 <- glm(crit_part ~ Inst_Cred_Gallup + House_distance_dim1 + AuthSex + AuthRank,
    family=binomial(link="logit"),
    data=polaradjdataset
    )

summary(mod4)
tidy(mod4)
glance(mod4)
```

```{r regression table, include=TRUE, echo=FALSE, results="asis"}
stargazer(mod3, mod4, 
          title="Table 3: Logistic Regression Results", 
          column.labels = c('Legislative Activity, Criticize, or Partisan','Criticize or Partisan'),
          covariate.labels = c('Institutional Credibility', 'Congressional Polarization', 'Male', 'Mixed Authorship', 'Unknown Authorship', 'Rank'),
          align=TRUE)
